\Huge Literature Search Made Easy: Mining Online Archives for Research Topic Trends

### 2013-11-20 article_1.tex
^o^

\subsection*{Latent Dirichlet Allocation (LDA)}

@@

\subsection*{Dynamic Topic Model (DTM)}

\subsection*{Supervised Latent Dirichlet Allocation (sLDA)}

\section*{Experiments}

@@

>>>>

\subsection*{Latent Dirichlet Allocation (LDA)}
Latent Dirichlet Allocation (LDA) \cite{2} is a topic modeling algorithm which assumes that each document is a mixture of various topics, whose prior distribution takes a Dirichlet distribution. In LDA, the number of topics is given a priori.

@@

\subsection*{Dynamic Topic Model (DTM)}
Dynamic topic models (DTM) \cite{3} are generative models that can be used to analyze the evolution of topics of a collection of documents over time. It is an extension of LDA which can handle sequential documents.\newline
In LDA, both the order the words appear in a document and the order the documents appear in the corpus are oblivious to the model. Whereas words are still assumed to be exchangeable, in a dynamic topic model the order of the documents plays a fundamental role. More precisely, the documents are grouped by time slice (e.g.: years) and it is assumed that the documents of each group come from a set of topics that evolved from the set of the previous slice.
\subsection*{Supervised Latent Dirichlet Allocation (sLDA)}
Supervised latent Dirichlet allocation (sLDA) is a statistical model of labelled documents, which can be used to predict response values for new documents. In this project, we plan to use sLDA to model the number of citations of each paper, and predict the importance of new papers based on the fitted model.
\section*{Experiments}

@@

 \bibitem[3] {3}
  Blei, D. and Lafferty, J.
  \emph{Dynamic Topic Models}.
  Proceedings of the 23rd International Conference of Machine Learning ,
 Pittsburgh, PA,
 2006

 \bibitem[4] {4}
  Blei, D. and McAuliffe, J.
  \emph{Supervised Topic Models}.
